### 2016-12-13 poster/poster.tex
updating theano in center table

\bgroup
\def\arraystretch{1.1}
\setlength\tabcolsep{5mm}
\begin{tabular}{c|ccc}
Time & Dynet & TensorFlow & Theano \\ \hline
Convergence & 26h10m & 35h25m & (TBD)\\
Train epoch & x & 6h57m & 6h35m \\
Test epoch & x & 7m45s & 24m \\
Train batch & 1s & 5s & x \\
Test batch & < 1s & $<$1s & x \\
\end{tabular}
\egroup
\vspace{5pt}
}

>>>>

\bgroup
\def\arraystretch{1.1}
\setlength\tabcolsep{5mm}
\begin{tabular}{c|ccc}
Time & Dynet & TensorFlow & Theano \\ \hline
Convergence & 26h10m & 35h25m & (TBD)\\
Train epoch & x & 6h57m & 6h35m \\
Test epoch & x & 7m45s & 24m \\
Train batch & 1s & 5s & 1s \\
Test batch & < 1s & $<$1s & < 1s \\
\end{tabular}
\egroup
\vspace{5pt}
}
